%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}
\graphicspath{ {./images/}}
\usepackage{titlesec}

\usepackage[dvipsnames]{xcolor}
\usepackage[usenames, dvipsnames]{color}

\titleformat{\section}


\definecolor{pinkish}{RGB}{200, 134, 145}
\definecolor{purplelish}{RGB}{173, 133, 186}
\definecolor{blueish}{RGB}{149, 161, 195}
\definecolor{greenish}{RGB}{116, 161, 142}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{}{GWYN HENDER}{ 
\href{mailto: gwyn.hender@gmail.com}{ gwyn.hender@gmail.com } \\
\hspace{} 01 02 03 04 05 \\ 
https://github.com/
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.99\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\subsection{University of Southern California}
\descript{Masters in Computer Science} 
\location{\color{purplelish} Grad. June 2016 | Los Angeles, CA}
\sectionsep
\subsection{University of Michigan}
\descript{Bachelor of Science in Computer Science}
\location{\color{purplelish}Grad. June 2014 | Ann Arbor, MI}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Telecommunications Inc.}
\descript{| Back-End Engineer }
\location{\color{purplelish}September 2018 – Present | Los Angeles, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Write modern, tested, maintainable code for a diverse array of client and internal projects (Python, bash, JS)
\item Conduct design and code reviews, sign off code for push to production 
\item Work in an Agile environment and participate in team-led solutions
\end{tightemize}
\sectionsep

\runsubsection{Teachers R US}
\descript{| Teaching Assistant }
\location{\color{purplelish}September 2017 – May 2018 | Los Angeles, CA}
\begin{tightemize}
\item Helped students understand course content and explained topics like data structures (queues, stacks, linked lists and trees), object-oriented programming, recursion and algorithm run-time
\item Prepared and held weekly labs/tutorials, introducing students to Python and Racket syntax
\item Proctored and graded quizzes, test and exams
\end{tightemize}
\sectionsep

\runsubsection{First Job Inc.}
\descript{| Software Engineering Intern }
\location{\color{purplelish}May 2016 - August 2017 | Los Angeles, CA}
\begin{tightemize}
\item Wrote bash and Lua scripts to locate and encrypt files identified by a specified extension to prevent tampering/modification, implemented a tiered system to grant privileges for modification (C++, Lua, Javascript, bash, openssl)
\item Designed and implemented a scraper to obtain Iguana instance logs and insert them to a central Postgres database, designed the schema and tested performance (Lua, Javascript, PostgreSQL)
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Personal Projects}
\runsubsection{Router/NAT}
\location{}
Implemented a simple router that received raw Ethernet  frames and ICMP packets forwarded them to the correct outgoing interface using a static routing table. Extended the router to be able to handle TCP and UDP connections. (C++)
\sectionsep

\runsubsection{Database Heaps}
\location{}
Worked on implementing different database store techniques: storing data using row store versus column store with the ability to scan, insert, update and delete records. Wrote bench-marking scripts to test the speed of block reads/writes. (C++)
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Technical Skills}
\subsection{Back-End}
Python \textbullet{} C++ / C \textbullet{} Java \textbullet{} Racket \textbullet{} Lua \textbullet{} Node.js \textbullet{} PostgreSQL \textbullet{} MySQL \textbullet{} Docker 
\sectionsep
\subsection{Front-End}
JavaScript ES6+ \textbullet{} CSS \textbullet{} HTML \textbullet{} React \textbullet{} Angular \textbullet{} Vue
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Coursework}
% {\color{blueish}Advanced Topics in Database Management} \textbullet{} Computer Networks (Theory \& Practice) \textbullet{} Algorithms \& Data Structures \textbullet{}  Operating Systems \textbullet{} Artificial Intelligence \textbullet{}  Functional Programming \textbullet{}  Statistics \\
% \sectionsep




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\end{document}  \documentclass[]{article}